Effects of the body force on the evacuation dynamics

### 2019-12-29 paper.tex
Update paper.tex

\noindent where $g(R_{ij}-r_{ij})$. $\Theta(R_{ij}-r_{ij})$ equals R_{ij}-r_{ij} 
if $R_{ij}>r_{ij}$ and vanished otherwise. 
$\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$ represents the difference 
between the tangential velocities of the sliding bodies (or between the 
individual and the walls).    \\

@@

\subsection{\label{sfm}The parameters setting}

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}\label{venn_2parameters}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}\label{venn_3parameters}}\\
\caption[width=0.47\columnwidth]{}
\label{flow_density}
\end{figure}

@@

>>>>

\noindent where $g(R_{ij}-r_{ij})$ equals $R_{ij}-r_{ij}$ if $R_{ij}>r_{ij}$ and 
vanished otherwise. $\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$ 
represents the difference between the tangential velocities of the sliding 
bodies (or between the individual and the walls).    \\

@@

\subsection{\label{parameters}The parameters setting}

The numerical setting of the parameters may affect the dynamics of the 
pedestrians. Some settings, however, yield similar collective dynamics. In 
order to investigate the similarities, we can introduce unit-less magnitudes 
and proceed straightforward as indicated in Appendix~\ref{appendix_1}. We 
realize from Appendix~\ref{appendix_1} that only three (unit-less) 
parameters  are the true ``control'' parameters for the collective dynamics. 
These are $\mathcal{A}$, $\mathcal{K}$, $\mathcal{K}_c$ as defined in 
Appendix~\ref{appendix_1}. Recall that $\mathcal{A}$ and $\mathcal{K}$ are 
precisely the same as in Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$ 
has been introduced due to the body force.   \\

The logical relations between the unit-less parameters and the ``individual'' 
parameters can be studied by means of the Venn diagrams exhibited in 
Fig.~\ref{venn_diagram}. The parameters $\mathcal{A}$, $\mathcal{K}$ and 
$\mathcal{K}_c$ are represented as intersecting sets, and the ``individual'' 
parameters are represented as elements within each set. The shared elements 
between $\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$ are placed inside de 
intersecting regions. \\

\begin{figure}[!htbp]
\centering

\subfloat[(a)]{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}
\label{venn_2parameters}}\

\subfloat[(b)]{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}
\label{venn_3parameters}}\\
\caption[width=0.47\columnwidth]{Venn diagrams for the unit-less parameters
appearing in the equation of motion (\ref{eqn_motion}) (see 
Appendix~\ref{appendix_1} for details). The sets correspond to 
$\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,\kappa\}$ and 
$\mathcal{K}_c=\{\tau/m,1/v_d,B,k\}$ (a) The Venn diagram representation if no 
body force is introduced in the SFM (only sets $\mathcal{A}$ and $\mathcal{K}$, 
as in Ref.~\cite{dorso_2019}). (b) The Venn diagram representation for the sets 
$\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$. }
\label{venn_diagram}
\end{figure}

The set of parameters introduced within the context of the SFM (see 
Section~\ref{background}) affects the collective dynamics. The setting for 
these parameters may change...\\

@@

\section{appendix_1}

The SFM description in Section~\ref{sfm} introduces seven parameters ($m$, 
$\tau$, $v_d$, $B$, $A$, $\kappa$ and $k$) attaining for the ``individual'' 
behavior of each pedestrian. The collective dynamic, however, requires a 
smaller set of parameters. In order to identify this smaller set, we introduce 
the following unit-less magnitudes\\

\begin{equation}
 \left\{\begin{array}{lcl}
         t' & = & t/\tau \\
         r' & = & r/B \\
         v' & = & v/v_d \\
        \end{array}\right.
\end{equation}

The equation of motion (\ref{eqn_motion}) can be written in terms of these 
(unit-less) magnitudes, while only three (reduced) parameters are needed.\\

\begin{equation}
 \displaystyle\frac{d\mathbf{v}'}{dt'}=
 \hat{\mathbf{e}}_d-\mathbd{v}'+\mathcal{A}\,e^{R'-r'}\,
 \hat{\mathbf{n}}+g(R'-r')\,\bigg[\mathcal{K}\,(\Delta\mathbf{v}'\cdot
 \hat{\mathbf{t}})\,\hat{\mathbf{t}}+\mathbf{K}_c\,\hat{\mathbf{n}}\bigg]
\end{equation}

\noindent where the smaller set ($\mathcal{A}$,$\mathcal{K}$,$\mathcal{K}_c$) 
means\\

\begin{equation}
 \mathcal{A}=\displaystyle\frac{A\,\tau}{m\,v_d}\ \ \ \ , \ \ \ \ 
 \mathcal{K}=\displaystyle\frac{\kappa\,B\,\tau}{m}\ \ \ \ , \ \ \ \
 \mathcal{K}_c=\displaystyle\frac{k\,B\,\tau}{m}
\end{equation}

Notice that the SFM will arrive to similar collective dynamics whenever the 
reduced set ($\mathcal{A}$,$\mathcal{K}$,$\mathcal{K}_c$) remains unchanged 
(although some ``individual'' parameters are allowed to change). For a deep 
explanation on the meaning  of the set 
($\mathcal{A}$,$\mathcal{K}$,$\mathcal{K}_c$) see Section~\ref{parameters}. \\
